%
% pScheduler Archiver Guide for RabbitMQ
%

\def\archivername{rabbitmq}


% TODO: Add titlepage to the options.
\documentclass[10pt]{article}

\input pscheduler-tex.tex

\DRAFT

\title{pScheduler Archiver Guide: {\it \archivername}}
\author{The perfSONAR Development Team}


\begin{document}
\maketitle


%
% INTRODUCTION
%

\section{Introduction}

The {\tt \archivername} archiver sends a raw JSON result to RabbitMQ.

This document describes schema version {\tt 1}.


%
% ARCHIVER DATA
%

\section{Archiver Data}

The {\tt data} object in the archiver specification may contain any of
the following:

\typeditem{_url}{URL} A URL to use in connecting to RabbitMQ.  The
format for the URL is described in the Pika documentation at {\tt
  https://pika.readthedocs.io/en/0.10.0/modules/parameters.html\#urlparameters},
but the general format is {\tt
  amqp://username:password@host:port/virtualhost[?query-string]}.

\typeditem{exchange}{String} The exchange to use in posting the
result.  If not provided, the empty string will be used.

\typeditem{routing-key}{String} The routing key to be used in
publishing the result to the queue.  If not provided, the empty string
will be used.

\typeditem{template}{AnyJSON} An optional JSON template used to
construct the JSON which will be sent to the queue.  Any pair having a
string value of {\tt __RESULT__} will have the result replaced with
the JSON object provided to the archiver.  If not provided, the
standard JSON format for the result will be sent to the queue.

\typeditem{retry-policy}{RetryPolicy} The policy for additional
attempts to archive the run after failures.


\example
\begin{lstlisting}[language=json]
{
    "_url": "amqp://netmonitor:mumblemumble@mq.example.com/",
    "routing-key": "perfsonar",
    "template": {
        "network": "backbone",
        "region": "central",
        "measurement": "__RESULT__"
    },
    "retry-policy": [
        { "attempts": 4,  "wait": "PT15S" },
        { "attempts": 5,  "wait": "PT1M" }
    ]
}
\end{lstlisting}

\end{document}
