%
% pScheduler Test Guide for Clock
%

\def\testname{clock}


% TODO: Add titlepage to the options.
\documentclass[10pt]{article}

\input pscheduler-tex.tex

\DRAFT

\title{pScheduler Test Guide: {\it \testname}}
\author{The perfSONAR Development Team}


\begin{document}
\maketitle


%
% INTRODUCTION
%

\section{Introduction}

The {\tt \testname} test measures the difference in time between the
clock on the local host and that on a remote host.

This document describes schema version {\tt 1}.


\subsection{Participants}

This test includes the following participants:

\begin{center}
\begin{tabular}{|c|c|}
\hline
{\bf Number} & {\bf Role} \\
\hline
{\tt 0} & Originator \\
\hline
\end{tabular}
\end{center}



%
% TEST SPECIFICATION
%

\section{Test Specification Format}

\subsection{Description}

The test specification consists of a single JSON object containing the
pairs below.  \seejson

\typeditem{schema}{Cardinal} The schema version of this specification.

\typeditem{dest}{Host} The network address or hostname of the receiver.

\typeditem{source}{Host} The network address or hostname of the
interface to use.

\typeditem{source-node}{Host} The network address or hostname of the
pScheduler instance which will serve as the originator.

\typeditem{timeout}{Duration} Amount of time to wait for a response
from each host.



\subsection{Example}
\begin{lstlisting}[language=json]
{
    "schema": 1,
    "dest": "somehost.example.org",
    "timeout": "PT5S"
}
\end{lstlisting}



%
% RESULT FORMAT
%

\section{Result Format}

\subsection{Description}
The result consists of a single JSON object containing the pairs
below.  \seejson

\typeditem{succeeded}{Boolean} Whether or not the test was a success.

\typeditem{local}{ClockState} The state of the originating system's
clock.

\typeditem{remote}{ClockState} The state of the remote (destination)
system's clock.

\typeditem{difference}{Duration} The difference in time between the
two clocks.

\subsection{Example}
\begin{lstlisting}[language=json]
{
    "schema": 1,

    "succeeded": true,
    "local": {
        "time": "2017-02-05T16:41:10.119931+00:00",
        "synchronized": true,
        "source": "ntp",
        "reference": "secondary reference (2) from 10.19.54.6",
        "offset": 6.6041946411132812e-05
    },
    "remote": {
        "time": "2017-02-05T08:41:50.424743-08:00",
        "synchronized": true,
        "source": "ntp",
        "reference": "secondary reference (2) from 10.62.7.91",
        "offset": 3.3817936411132812e-05
    },
    "difference": "PT0.422658S"
}
\end{lstlisting}


\end{document}
